### 2020-05-31 writeup/setup.tex
sec 2

Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$, which captures how similar $\beta_1$ and $\beta_2$ are.
Hence, the bias of $\hat{\beta}_t^{\MTL}$ introduces a negative effect from adding the source labels.
Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, which is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
This part introduces a positive variance reduction effect from adding the source labels.
Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined by the bias-variance tradeoff of
(i) the negative effect from model shift bias.
(ii) the positive effect from variance reduction;
In order to analyze the tradeoff, we develop the following technical tool, which provides a tight bound for equation \eqref{eq_te_var}.

>>>>

Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$, which captures how similar $\beta_1$ and $\beta_2$ are.
Hence, the bias of $\hat{\beta}_t^{\MTL}$ introduces a negative effect from adding the source labels.
Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, which is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
%This part introduces a positive variance reduction effect from adding the source labels.
Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the bias-variance tradeoff!
%(i) the negative effect from model shift bias.
%(ii) the positive effect from variance reduction;
In order to analyze the tradeoff, we develop the following technical tool, which provides a tight bound for equation \eqref{eq_te_var}.
